Overview

### 2023-10-03 vig_body.Rmd
Correct all docs [no ci]
Fix #76

H0: MP is not better than 1/ n\_top\_terms

H1: MP is better than 1/ n\_top\_terms

@@

Create an oolong object, clone it for another coder. According to Song et al. (Forthcoming), you should at least draw 1% of your data.

@@

The textual output contains the Krippendorff's alpha of the codings by your raters. In order to claim validity of your target value, you must first establish the reliability of your gold standard. Song et al. [Forthcoming] suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.

>>>>

H0: MP is not better than 1/ (n\_top\_terms + 1)

H1: MP is better than 1/ (n\_top\_terms + 1)

@@

Create an oolong object, clone it for another coder. According to Song et al. (2020), you should at least draw 1% of your data.

@@

The textual output contains the Krippendorff's alpha of the codings by your raters. In order to claim validity of your target value, you must first establish the reliability of your gold standard. Song et al. (2020) suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.
